Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-05-27 manuscripts/manuscript.Rmd
tweaks

A worthwhile modeling extension suggested by our results would be to
examine the implications of policy adjustment costs for risks of stock
collapse. Examining risks of stock collapse is not possible with the
Reed model formulation that we followed here but would be worthwhile
in light of our finding that the variance and autocorrelation in stock
sizes through time can be affected when accounting for costs of policy
adjustment. Both are properties known in other modeling settings to
be associated with changes to the risk of extinction or of transitions
between alternative stable states [@Scheffer2009]. This highlights the risk
that changes in management policies can either mimic or mask such possible
early warning signs of sudden transitions, and points to another way
in which more context is needed before such approaches can be useful to
management [@Boettiger2013].

@@

This work was assisted through participation in "Pretty Darn Good Control"
Investigative Workshop at the National Institute for Mathematical and
Biological Synthesis, sponsored by the National Science Foundation through
NSF Award #DBI-1300426, with additional support from The University of
Tennessee, Knoxville.  The authors acknowledge helpful discussions and
input from working group co-organizers Megan Donahue and Carl Toews, and
participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
Iadine Chades and Mandy Karnauskas.  We also acknowledge the support of
NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572) & the
ARC Centre of Excellence for Environmental Decisions to MB.

>>>>

A worthwhile modeling extension suggested by our results would be to
examine the implications of policy adjustment costs for risks of stock
collapse. This includes models with larger stochasticity as well as model
formulations that can permit alternative stable states.
Examining risks of stock collapse is not possible with the
Reed model formulation that we followed here (both cases are inconsistent
with the assumptions of @Reed1974) but would be worthwhile
in light of our finding that the variance and autocorrelation in stock
sizes through time can be affected when accounting for costs of policy
adjustment. Both are properties known in other modeling settings to
be associated with changes to the risk of extinction or of transitions
between alternative stable states [@Scheffer2009]. This highlights the risk
that changes in management policies can either mimic or mask such possible
early warning signs of sudden transitions, and points to another way
in which more context is needed before such approaches can be useful to
management [@Boettiger2013].

@@

This work was assisted through participation in "Pretty Darn Good Control"
Investigative Workshop at the National Institute for Mathematical and
Biological Synthesis, sponsored by the National Science Foundation through
NSF Award #DBI-1300426, with additional support from The University of
Tennessee, Knoxville.  The authors acknowledge helpful discussions and
input from working group co-organizers Megan Donahue and Carl Toews, and
participants Marie-Josee Fortin, Dan Ryan, Frank Doyle, Claire Paris,
Iadine Chades and Mandy Karnauskas, as well as the two anonymous reviewers
whose feedback strengthened this paper.  We also acknowledge the support of
NSF Grant DBI-1306697 to CB and ARC DECRA (DE130100572) & the
ARC Centre of Excellence for Environmental Decisions to MB.
